quollr: An R Package for Visualizing 2-D Models from Nonlinear Dimension Reductions in High-Dimensional Space

### 2025-12-08 paper-quollr.Rmd
Started adding labels for figure 3

algofig <- bscols(
  htmltools::div(
    style = "
      display: flex;
      justify-content: center;     /* centers the grid horizontally */
      align-items: center;          /* optional: centers vertically if space allows */
      margin: 0 auto;
      padding: 0;
    ",
    htmltools::div(
      style = "
        display: grid;
        grid-template-columns: 1fr 1fr;
        gap: 0px;
        align-items: start;
        justify-items: center;
        margin: 0;
        padding: 0;
      ",
      htmltools::div(style = 'margin: 0; padding: 0;  height: 300px; width: 300px;', hex_grid_poly_scurve_int),
      htmltools::div(style = 'margin: 0; padding: 0; height: 350px; width: 400px;', hex_centroids_scurve_int),
      htmltools::div(style = 'margin: 0; padding: 0; height: 300px; width: 300px;', wireframe_scurve_int),
      htmltools::div(style = 'margin: 0; padding: 0; margin-left: 60px; height: 300px;', scurve_umap_model_vis_n)
    )
  ),
  device = "xs"
)

>>>>

algofig <- bscols(
  htmltools::div(
    style = "
      display: flex;
      justify-content: center;     /* centers the grid horizontally */
      align-items: center;          /* optional: centers vertically if space allows */
      margin: 0 auto;
      padding: 0;
    ",
    htmltools::div(
      style = "
        display: grid;
        grid-template-columns: 1fr 1fr;
        gap: 0px;
        align-items: start;
        justify-items: center;
        margin: 0;
        padding: 0;
      ",
      htmltools::div(style = 'margin: 0; padding: 0;  height: 300px; width: 300px; text-align: left;', htmltools::h4("a"), hex_grid_poly_scurve_int),
      htmltools::div(style = 'margin: 0; padding: 0; height: 350px; width: 400px; text-align: left;', htmltools::h4("b"), hex_centroids_scurve_int),
      htmltools::div(style = 'margin: 0; padding: 0; height: 300px; width: 300px;  text-align: left;', htmltools::h4("c"), wireframe_scurve_int),
      htmltools::div(style = 'margin: 0; padding: 0; margin-left: 60px; height: 300px;  text-align: left;', htmltools::h4("d"), scurve_umap_model_vis_n)
    )
  ),
  device = "xs"
)
